---
title: "Bayesian Inference"
output: html_notebook
author: "Maxime Keutgen"
---
## Introduction

This is an R notebook about Bayesian Inference. Let's start with an example. We are conducting a study on heart strokes. Historical studies show complication SICH. We want to estimate risk for SICH in ECASS 3. We have prior informations from two studies : ECASS 1 and ECASS 2, ECASS 2 says proportion of patients with SICH is $ 8/100 $.

The first preliminary results, in ECASS 3, tell us that out of 50 patients with strokes, 10 are affected by the SICH complication.

### Notation : 
 
* SICH incidence : $\theta$
* i.i.d Bernouilli rvs : $y_1,...,y_n$
* SICH : $y_1 = 1$, 0 otherwise.
* $y = \sum^{n}_{i=1} y_i \sim Bin(n,\theta)$
* $p(y|\theta) = {n\choose\theta} \theta^y (1-\theta)^{n-y}$ 

## The Frequentist paradigm

Let's get back for a moment to the good old frequentist paradigm. In this paradigm, we do not use any prior informations (asymptotic makes rrrr).  
```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}

```

